Toward single particle reconstruction without particle picking: Breaking the detection limit

### 2018-08-28 pnas/Towards.tex
Early noon session

Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR \TODO{the impossibility result should be in the theory section}. This fact has been recognized early on by the cryo-EM community. In particular, in an influential paper from 1995, Henderson~\cite{henderson1995limitations} investigates the following questions:
\begin{quote}
	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy? Given what has already been demonstrated in published work, this reduces to the question: what is the smallest size of molecule for which it is possible to determine from images of unstained molecules the five parameters needed to define accurately its orientation (three parameters) and position (two parameters) so that averaging can be performed?}
\end{quote}
In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). 
Joachim Frank voices a similar observation in his Nobel prize lecture: ``\emph{Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size: Particle Size > 3/[Contrast$^2\times $  Resolution (as length) $\times$ Critical Electron Dose]}''~\cite{frank2018single}. 
\TODO{As these two leaders of the cryo-EM community point out,} it is impossible to reconstruct small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, because the particles themselves cannot be picked from the micrographs.

@@

In this paper, we argue that there is a gap between the two questions in Henderson's quoted excerpt above, and that one may be able to exploit it to design better reconstruction algorithms.
Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done. Our main message is that the limits particle picking imposes on molecule size do not translate into limits on particle reconstruction.

As a proof of concept, we study a toy model for which it is easier to convey the mathematical principles. 
In this toy model, an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
The goal is to estimate the planted image. The task is interesting in particular when the SNR is low enough that particle picking cannot be done reliably. 
This problem is interesting of its own as it appears in other scientific applications, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.

In order to recover the image, we use autocorrelation analysis. In a nutshell, we relate the autocorrelations of the micrographs to the autocorrelations of the image.
For any noise level, these autocorrelations can be estimated to any desired accuracy, provided that we get to observe sufficiently many image occurrences and the latter are separated in the micrograph. Importantly, there is no need to detect individual image occurrences. The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data. These directly yield estimates for the autocorrelations of the image. To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem.

Autocorrelation analysis for 3-D reconstruction, under the assumption of perfect particle picking,  was first proposed by Zvi Kam~\cite{kam1980reconstruction}. 
In this work, we derive the mathematical relation between the autocorrelations of the micrographs and the 3-D volume under some simplifying conditions.
We show a few numerical examples and draw the future developments required to make this method applicable on real data. \TODO{This paragraph would be changed according to the final results we will show}

Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}. In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged. In~\cite{shatsky2009method}, it was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template. In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles may influence the reconstructed structure. This model bias is common to all particle picking methods based on template matching. In our approach, no templates or human intervention are required, thus significantly reducing concerns about model bias. %
%To illustrate the possibility to estimate a signal without detecting its locations, we first discuss a toy model for which it is easier to convey the mathematical principles. 
%In this toy model, an unknown image appears numerous times at unknown locations in several micrographs, each affected by additive Gaussian noise---see Figure~TKTK for an illustration.
%The goal is to estimate the planted image. The task is interesting in particular when the SNR is low enough that particle picking cannot be done reliably. 
%This problem is interesting of its own as it appears in other scientific applications, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}. We study it in more details, including an extension to multiple planted images, in a companion paper~\cite{bendory2018estimation}.

@@

In general, for a signal $z$ of length $m$, the autocorrelation of order $q \geq 1$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
\begin{align}
a_z^q[\ell_1,\ldots,\ell_{k-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
\label{eq:ac_general}
\end{align}
where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
Explicitly, the first-, second- and third-order autocorrelations are given by
\begin{align} 
a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
\end{align}
The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
$
%\begin{align*}
%a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
%\end{align*}
%Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK--I think it was commented in the latex} (respectively) non-trivial distinct real numbers, generically.
%
%For the special case $K = 1$ where a single signal $x = x_1$ must be recovered, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, so that we treat it first. It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$, and let
%\begin{align}
%\gamma & = \frac{M L}{N}
%\end{align}
%denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The spacing constraint~\eqref{eq:spacing} imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.

@@

\TODO{Here the cryo-EM setup shows up}

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=.68]{Einstein_progress} (left) power spectrum estimation error (right) RRR error after fixed number of 1000 iterations.
	\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
\end{figure}

@@

@@

\paragraph{3-D experiments.}

@@

{\bf Case 2:} $0=\ell_2 < \ell_1$. Term (2) is an average of products of the form $\ep[i]^2\ep[i+\ell_1]$, which have mean zero; consequently, term (2) converges to 0 almost surely. The same argument as for Case 1 shows that (3) and (5) also converge to 0. For term (4), we write:
%
\begin{align}
%
&\frac{1}{N}\sum_{j=1}^{M} 
\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]
\nonumber \\
&= \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-1}x[i] \frac{1}{M}\sum_{j=1}^{M} \ep[s_j+i-\ell_1]^2
\xrightarrow{N\to\infty} \gamma \frac{1}{L} \sum_{i=0}^{L-1}x[i] \sigma^2 = \gamma a_x^1 \sigma^2.
%
\end{align}

@@

This completes the proof of \eqref{eq:data_ac}.

@@

Now, suppose that the quadratics are dependent. Then, $\frac{\mathcal{B}}{\mathcal{C}} =\frac{\mathcal{E}}{\mathcal{F}} $, or, 	
\begin{equation*}
La_y^2[0] - (2L+1)(a_y^1)^2 - La_y^2 = (a_y^1)^2(3-6L)
\end{equation*}
Rearranging the equation and writing in terms of $x$ we get 
\begin{equation} \label{eq:cond}
4(L-1)\beta (a_x^1)^2  - \sum_{i=1}^{L-1} a_x^2[i] = 0.
\end{equation}	
For generic $x$,  this polynomial equation is not satisfied. Therefore,  the equations are independent. 
More than that, for any nonzero $x$, $(a_x^1)^2 >\sum_{i=1}^{L-1} a_x^2[i]$. Therefore, if $4(L-1)\beta \geq 1$, or,
\begin{equation*}
\beta \geq \frac{1}{4(L-1)},
\end{equation*}
the condition~\eqref{eq:cond} cannot be satisfied for any signal.

\section{Autocorrelations of the cryo-EM problem}

@@

For the third moments, we get 8 terms:
\[\begin{aligned} 
&a^3_\II[\Bell_1, \Bell_2] =
\underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i+\Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(1)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\varepsilon[\mb i+\Bell_1]\varepsilon[\mb i + \Bell_2]}_{(2)}\\ 
&+ \underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(3)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\varepsilon[\mb i + \Bell_2]}_{(4)}\\
&+ \underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\widetilde\II[\mb i + \Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(5)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell_1]\varepsilon[\mb i + \Bell_2]}_{(6)}\\
&+ \underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\varepsilon[\mb i + \Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(7)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\widetilde\II[\mb i + \Bell_1]\varepsilon[\mb i + \Bell_2]}_{(8)}.
\end{aligned}\]
We address these terms one by one:
\begin{itemize}
	\item  Term (1) is treated by~\eqref{eq:general_moment} for $p=3$;
	\item Term (2) is the third-order autocorrelation of  pure noise  which vanishes in the limit; 
	\item Terms (3)-(5) depend linearly on the noise and hence
	vanish in the limit;
	\item For term (6), if $\Bell_1\neq \Bell_2$ the term
	vanishes in the limit. If $\Bell_1 = \Bell_2$ then
	\[ \begin{aligned}
	\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell]^2
	&= \frac{MP^2}{N^2}\cdot\frac{1}{MP^2}\sum_{t=1}^{M}\sum_{\mb i\in\mc S_t}I_{\omega_t}[\mb i]\varepsilon[\mb i + \Bell]^2 
	\\& \to \gamma\sigma^2 \langle a^1_{I_{\omega}}\rangle_{\omega}, %\gamma\mathbb{E}_{\omega, \varepsilon}[\varepsilon^2I_{\omga}]\\
	%&= \gamma\sigma^2\mathbb{E}[m_1[I_{\omega}]]\\ 
	%&= \gamma\sigma^2Lm_1[\phi],
	\end{aligned}\]
	where $\langle a^1_{I_{\omega}}\rangle_{\omega}$ is the mean of the volume. 
	\item  Terms (7) and (8) contribute $\delta$ functions similar to (6).
\end{itemize}
Thus, we conclude that
\begin{equation} \label{eq:third_order_ac_micro_volume}
a^3_\II[\Bell_1, \Bell_2] \to \gamma\langle
a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega} +
\gamma\sigma^2\langle a^1_{I_{\omega}}\rangle_{\omega}\Big(\delta[\Bell_1 - \Bell_2] +
\delta[\Bell_1] + \delta[\Bell_2]\Big),
\end{equation}
where the second term is the bias $b_3[\Bell_1,\Bell_2]$.
Note that $\gamma\langle a^1_{I_{\omega}}\rangle_{\omega}$ is approximately the mean of the micrograph since  $a^1_\II \approx a^1_{\tilde\II} \approx \gamma\langle a^1_{I_{\omega}}\rangle_{\omega}$. Therefore, we do not need prior knowledge of $\gamma$ to effectively
debias the third-order autocorrelation.

@@

\TODO{=========== Tamir: Stopped here ===============}

\TODO{=========== NOT SURE WHAT IS THAT ===============}
\begin{align*}
&C_2^{(q)} = \int_0^1j_{\ell,s_1}(k)j_{\ell,s_2}(k)R_{0,q}(k)k\, dk\\
&C_3^{(k,q_1,q_2)}\ell_1,m_1,s_1;\ell_2,m_2,s_2;\ell_3,s_3):= (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\Bell]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\Bell]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\Bell]},
\end{align*}
and 
\begin{align*}
\rho_{\ell,N,s}^{(k,q)}&=\int_{\Bell}\Psi_{\ell,N,s}([\mb i+\Bell])\overline{\psi_{k,q}(\Bell)}.
\end{align*}

>>>>

Crucially, it can be shown that reliable detection of individual particles is impossible below a certain critical SNR. This fact has been recognized early on by the cryo-EM community. In particular, in an influential paper from 1995, Henderson~\cite{henderson1995limitations} investigates the following questions:
\begin{quote}
	\emph{For the purposes of this review, I would like to ask the question: what is the smallest size of free-standing molecule whose structure can in principle be determined by phase-contrast electron microscopy? Given what has already been demonstrated in published work, this reduces to the question: what is the smallest size of molecule for which it is possible to determine from images of unstained molecules the five parameters needed to define accurately its orientation (three parameters) and position (two parameters) so that averaging can be performed?}
\end{quote}
In that paper and in others that followed (e.g.,~\cite{glaeser1999electron}), it was established that particle picking is impossible for molecules below a certain weight (below $\sim$50 kDa). 
Joachim Frank voices a similar observation in his Nobel prize lecture: ``\emph{Using the ribosome as an example, it became clear from the formula we obtained that the single-particle approach to structure research was indeed feasible for molecules of sufficient size: Particle Size > 3/[Contrast$^2\times $  Resolution (as length) $\times$ Critical Electron Dose]}''~\cite{frank2018single}. 
\TODO{As these two leaders of the cryo-EM community point out,} it is impossible to reconstruct small molecules by any of the existing computational pipelines for single particle analysis in cryo--EM, because the particles themselves cannot be picked from the micrographs.

@@

In this paper, we argue that there is a gap between the two questions in Henderson's quoted excerpt above, and that one may be able to exploit it to design better reconstruction algorithms.
Specifically, the impossibility of particle picking does not necessarily imply impossibility of particle reconstruction.
Indeed, the aim is only to reconstruct the molecule: estimating the locations of the particles in the micrograph is merely a helpful intermediate stage when it can be done. Our main message is that the limits particle picking imposes on molecule size do not necessarily  translate into limits on particle reconstruction.

As a proof of concept, we study a toy model for which it is easier to convey the mathematical principles. 
In this toy model, an unknown image appears multiple times at unknown locations in each of several micrographs, each affected by additive Gaussian noise---see Figure~\ref{fig:micro_example} for an illustration.
The goal is to estimate the planted image. The task is challenging in particular when the SNR is low enough that particle picking (identifying the locations of each image in each micrograph) cannot be done reliably. 
This problem is interesting of its own as it appears in other scientific applications, such as spike sorting~\cite{lewicki1998review}, passive radar~\cite{gogineni2017passive} and system identification~\cite{ljung1998system}.

In order to recover the image, we use autocorrelation analysis. Specifically, we relate the autocorrelations of the micrographs to the autocorrelations of the image.
For any noise level, these autocorrelations can be estimated to any desired accuracy, provided that we  observe sufficiently many image occurrences and the latter are separated in the micrograph. Importantly, there is no need to detect individual image occurrences. The autocorrelations of the micrographs are straightforward to compute and require only one pass over the data. These directly yield estimates for the autocorrelations of the image \TODO{Will: This is not quite true, because of the gamma parameter}. To estimate the image itself from its estimated autocorrelations, we solve a nonlinear inverse problem.

Autocorrelation analysis for 3-D reconstruction, under the assumption of perfect particle picking,  was first proposed by Zvi Kam~\cite{kam1980reconstruction}. 
In this work, we derive the mathematical relation between the autocorrelations of the micrographs and the 3-D volume under some simplifying conditions.
We show a few numerical examples and outline the future developments required to make this method applicable on real data. \TODO{This paragraph would be changed according to the final results we will show}

Another interesting feature of the described approach pertains to model bias, whose importance in cryo-EM was stressed by a number of authors~\cite{shatsky2009method,vanheel1992correlation,henderson2013avoiding,vanheel2013finding}. In the classical ``Einstein from noise'' experiment, multiple realizations of pure noise are aligned to a picture of Einstein using template matching and then averaged. In~\cite{shatsky2009method}, it was shown that the averaged noise rapidly becomes remarkably similar to the Einstein template. In the context of cryo--EM, this experiment exemplifies how prior assumptions about the particles may influence the reconstructed structure. This model bias is common to all particle picking methods based on template matching. In our approach, no templates or human intervention are required, thus significantly reducing concerns about model bias. %

@@

In general, for a signal $z$ of length $m$, the autocorrelation of order $q \geq 1$ is given for any integer shifts $\ell_1, \ldots, \ell_{q-1}$ by
\begin{align}
a_z^q[\ell_1,\ldots,\ell_{k-1}]  & = \frac{1}{m} \sum_{i=-\infty}^{+\infty} z[i]z[i+\ell_1]\cdots z[i+\ell_{q-1}],
\label{eq:ac_general}
\end{align}
where indexing of $z$ out of the range $0, \ldots, m-1$ is zero-padded.
For our purposes, this will be applied both to $x$ (of length $L$) and to $y$ (of length $N$).
Explicitly, the first-, second- and third-order autocorrelations are given by \TODO{we may want to remove these explicit formulas}
\begin{align} 
a_z^1 & = \frac{1}{m} \sum_{i=0}^{m-1} z[i], \nonumber\\
a_z^2[\ell] & = \frac{1}{m} \sum_{i = \max\{0, -\ell\}}^{m-1 + \min\{0, -\ell\}} z[i]z[i+\ell], \nonumber\\
a_z^3[\ell_1,\ell_2] & = \frac{1}{m} \sum_{i = \max\{0, -\ell_1, -\ell_2\}}^{m-1 + \min\{0, -\ell_1, -\ell_2\}} z[i]z[i+\ell_1]z[i+\ell_2]. \label{eq:ac_special}
\end{align}
The autocorrelation functions have symmetries. Specifically, $a_z^2[\ell] = a_z^2[-\ell]$, and
$a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
$
%\begin{align*}
%a_z^3[\ell_1,\ell_2] = a_z^3[\ell_2,\ell_1]=a_z^3[-\ell_1,\ell_2-\ell_1].
%\end{align*}
%Taking these symmetries into consideration, one can show that $a_z^1, a_z^2$ and $a_z^3$ contain \TODO{TKTK--I think it was commented in the latex} (respectively) non-trivial distinct real numbers, generically.
%
%For the special case $K = 1$ where a single signal $x = x_1$ must be recovered, the relation between autocorrelations of the micrograph and those of $x$ is particularly simple, so that we treat it first. It is useful to introduce some notation: let $M$ denote the number of occurrences of $x$ in $y$, and let
%\begin{align}
%\gamma & = \frac{M L}{N}
%\end{align}
%denote the density of $x$ in $y$ (that is, the fraction of entries of $y$ occupied by occurrences of $x$.) The spacing constraint~\eqref{eq:spacing} imposes $\gamma\leq\frac{L}{2L-1}\approx 1/2$.

@@

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=.55]{Einstein_progress} (left) power spectrum estimation error (right) RRR error after fixed number of 1000 iterations.
	\caption{\label{fig:error_per_micro} Relative root mean square error of the estimate of Einstein's image as a function of the number of observed micrographs (logarithmic scale along both axes.)}
\end{figure}

@@

The application of autocorrelation analysis to cryo-EM follows the same mathematical principles.
The derivation of the first three autocorrelations of the micrographs and their relations to the volume itself are provided in Appendix~\ref{sec:ac_cryo}.
In particular, numerical evidence suggests that the third-order autocorrelation uniquely determines the 3-D volume. Figure~TKTK shows recovery of the 3-D volume from the clean autocorrelations. The details of the reconstruction algorithm are given in Appendix~\ref{sec:numeric_details}.
Unfortunately, the mapping between the autocorrelations and volume seems to be ill-conditioned, preventing recovery from noisy data. 
In the next section, we outline how we suggest to overcome the ill-conditioning in future work.

While we cannot provide a 3-D reconstruction from noisy data with the current algorithm, our method can be easily applied to the problem of deciding whether a micrograph contains projections or merely pure noise---a problem considered in classical works in statistics (e.g.,~\cite{donoho2004higher}) and debates in the cryo-EM community~\cite{henderson2013avoiding}.
This task can be performed by considering solely the recovered $\gamma$ (the fraction of pixels occupied by projections in the micrograph), estimated as part of the recovery algorithm.
Figure~\ref{fig:cryo_detection} presents excerpts \TODO{sections?} of two noisy micrographs, only one of which contains projections.
In the presence of projections, the estimated $\gamma$ was $0.12$, corresponding to approximately $6784$ projections. 
On the hand, the estimated $\gamma$ drops to $10^{-5}$ for the pure noise micrograph, corresponding to less than one projection.
%
%Under the experimental parameters (see Section~\ref{sec:numeric_details}), such values of $\gamma$ predict  in the informative micrograph and less than one projection in the pure noise scenario.

\begin{figure*}[h]
	\centering
	\begin{subfigure}[h]{0.3\textwidth}
		\centering
		\includegraphics[scale=0.4]{pure_noise_micrograph_cutout.eps}
		\caption{An excerpt of the pure noise micrograph}
	\end{subfigure} \hspace{2pt}
	\begin{subfigure}[h]{0.3\textwidth}
		\centering
		\includegraphics[scale=0.4]{noisy_micrograph_cutout.eps}
		\caption{An excerpt of the clean micrograph in right panel perturbed by the noise in the left panel.}
	\end{subfigure} \hspace{2pt}
	\begin{subfigure}[h]{0.3\textwidth}
		\centering
		\includegraphics[scale=0.4]{clean_micrograph_cutout.eps}
		\caption{An excerpt of the clean micrograph}
	\end{subfigure}
	\caption{\label{fig:cryo_detection} All micrographs are of size $7420^2$ pixels and the projections are taken from a volume of size $31^3$. The added noise was drawn from i.i.d.\ Gaussian distribution with zero mean and standard deviation $25$, corresponding to an SNR below $1/1024$.  
		The noise realization is identical in both micrographs. }	
\end{figure*}

@@

\paragraph{3-D experiments.}
For the experiment in Figure~TKTK, we computed the analytical first three autocorrelations of the volume according to~TKTK.

@@

{\bf Case 2:} $0=\ell_2 < \ell_1$. Term (2) is an average of products of the form $\ep[i]^2\ep[i+\ell_1]$, which have mean zero; consequently, term (2) converges to 0 almost surely. The same argument as for Case 1 shows that (3) and (5) also converge to 0. For term (4), we write:
%
\begin{align}
%
&\frac{1}{N}\sum_{j=1}^{M} 
\sum_{i=0}^{L-1} \ep[s_j+i-\ell_1]x[i]\ep[s_j+ i+\ell_2-\ell_1]
\nonumber \\
&= \frac{ML}{N}\frac{1}{L}\sum_{i=0}^{L-1}x[i] \frac{1}{M}\sum_{j=1}^{M} \ep[s_j+i-\ell_1]^2
\\& \xrightarrow{N\to\infty} \gamma \frac{1}{L} \sum_{i=0}^{L-1}x[i] \sigma^2 = \gamma a_x^1 \sigma^2. \nonumber
%
\end{align}

@@

This completes the proof.

@@

Now, suppose that the quadratics are dependent. Then, $\frac{\mathcal{B}}{\mathcal{C}} =\frac{\mathcal{E}}{\mathcal{F}} $, or, 	
\begin{equation*}
La_y^2[0] - (2L+1)(a_y^1)^2 - La_y^2 = (a_y^1)^2(3-6L).
\end{equation*}
Rearranging the equation and writing in terms of $x$ we get 
\begin{equation} \label{eq:cond}
4(L-1)\beta (a_x^1)^2  - \sum_{i=1}^{L-1} a_x^2[i] = 0.
\end{equation}	
For generic $x$,  this polynomial equation is not satisfied. Therefore,  the equations are independent. 
More than that, for any nonzero $x$, $(a_x^1)^2 >\sum_{i=1}^{L-1} a_x^2[i]$. Therefore, if $4(L-1)\beta \geq 1$, or,
\begin{equation*}
\beta \geq \frac{1}{4(L-1)},
\end{equation*}
the condition~\eqref{eq:cond} cannot be satisfied for any signal.

\section{Autocorrelations of the cryo-EM problem} \label{sec:ac_cryo}

@@

For the third moments, we get 8 terms:
\[\begin{aligned} 
&a^3_\II[\Bell_1, \Bell_2]  \\&
 = \underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i+\Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(1)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\varepsilon[\mb i+\Bell_1]\varepsilon[\mb i + \Bell_2]}_{(2)}\\ 
&+ \underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(3)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\widetilde\II[\mb i + \Bell_1]\varepsilon[\mb i + \Bell_2]}_{(4)}\\
&+ \underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\widetilde\II[\mb i + \Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(5)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell_1]\varepsilon[\mb i + \Bell_2]}_{(6)}\\
&+ \underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\varepsilon[\mb i + \Bell_1]\widetilde\II[\mb i + \Bell_2]}_{(7)} +
\underbrace{\frac{1}{N^2}\sum_{\mb i}\varepsilon[\mb i]\widetilde\II[\mb i + \Bell_1]\varepsilon[\mb i + \Bell_2]}_{(8)}.
\end{aligned}\]
We address these terms one by one:
\begin{itemize}
	\item  Term (1) is treated by~\eqref{eq:general_moment} for $p=3$;
	\item Term (2) is the third-order autocorrelation of  pure noise  which vanishes in the limit; 
	\item Terms (3)-(5) depend linearly on the noise and hence
	vanish in the limit;
	\item For term (6), if $\Bell_1\neq \Bell_2$ the term
	vanishes in the limit. If $\Bell_1 = \Bell_2$ then
	\[ \begin{aligned}
	\frac{1}{N^2}\sum_{\mb i}\widetilde\II[\mb i]\varepsilon[\mb i + \Bell]^2
	&= \frac{MP^2}{N^2}\cdot\frac{1}{MP^2}\sum_{t=1}^{M}\sum_{\mb i\in\mc S_t}I_{\omega_t}[\mb i]\varepsilon[\mb i + \Bell]^2 
	\\& \to \gamma\sigma^2 \langle a^1_{I_{\omega}}\rangle_{\omega}, %\gamma\mathbb{E}_{\omega, \varepsilon}[\varepsilon^2I_{\omga}]\\
	%&= \gamma\sigma^2\mathbb{E}[m_1[I_{\omega}]]\\ 
	%&= \gamma\sigma^2Lm_1[\phi],
	\end{aligned}\]
	where $\langle a^1_{I_{\omega}}\rangle_{\omega}$ is the mean of the volume. 
	\item  Terms (7) and (8) contribute $\delta$ functions similar to (6).
\end{itemize}
Thus, we conclude that
\begin{equation} \label{eq:third_order_ac_micro_volume}
a^3_\II[\Bell_1, \Bell_2] \to \gamma\langle
a^3_{I_{\omega}}[\Bell_1, \Bell_2]\rangle_{\omega} +
\gamma\sigma^2\langle a^1_{I_{\omega}}\rangle_{\omega}\Big(\delta[\Bell_1 - \Bell_2] +
\delta[\Bell_1] + \delta[\Bell_2]\Big),
\end{equation}
where the second term is the bias $b_3[\Bell_1,\Bell_2]$.
Note that $\gamma\langle a^1_{I_{\omega}}\rangle_{\omega}$ is approximately the mean of the micrograph since  $a^1_\II \approx a^1_{\tilde\II} \approx \gamma\langle a^1_{I_{\omega}}\rangle_{\omega}$. Therefore, we do not need prior knowledge of $\gamma$ to effectively
debias the third-order autocorrelation.

@@

%\TODO{=========== Tamir: Stopped here ===============}

%\TODO{=========== NOT SURE WHAT IS THAT ===============}
%\begin{align*}
%&C_2^{(q)} = \int_0^1j_{\ell,s_1}(k)j_{\ell,s_2}(k)R_{0,q}(k)k\, dk\\
%&C_3^{(k,q_1,q_2)}\ell_1,m_1,s_1;\ell_2,m_2,s_2;\ell_3,s_3):= (-1)^{m_1+m_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ m_1 & m_2 & -m_1-m_2\end{array}\right)\\
%&\times \sum_{N_1=-\ell_1}^{\ell_1}\sum_{N_2=-\ell_2}^{\ell_2}(-1)^{N_1+N_2}\left(\begin{array}{ccc}\ell_1 & \ell_2  & \ell_3\\ N_1 & N_2 & -N_1-N2\end{array}\right)\frac{1}{L^2}\sum_{\mb i}\Psi_{\ell_1,N_1,s_1}[\Bell]\rho_{\ell_2,N_2,s_2}^{(k,q_1)}[\Bell]\overline{\rho_{\ell_3,N_1+N_2,s_3}^{(k,q_2)}[\Bell]},
%\end{align*}
%and 
%\begin{align*}
%\rho_{\ell,N,s}^{(k,q)}&=\int_{\Bell}\Psi_{\ell,N,s}([\mb i+\Bell])\overline{\psi_{k,q}(\Bell)}.
%\end{align*}
